Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-13 paper/paper.tex
update engines

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries.
\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}
We found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
For example, the latest version of ES specs~\cite{es6-spec} describes that,
the function \CodeIn{Number.toPrecision(precision)}, in general,
returns a String containing the Number value represented either 
in decimal exponential notation or in decimal fixed notation, 
if precision is defined~\cite{es6-toPrecision}. The Number object uses a 
property called

\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
due the capacity of a fuzzer add an infinite repetition statement. We expected that
each test process can running utmost 5 seconds, if exceed this condition we stop 
the process and add a output message of a TIMEOUT error.}
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO. Use the stacktraces to explain what is going on.}

@@

% bug high console output
This a case of a warning reported as HI priority, the Figure~\ref{} shows
the output console of V8 engine. We consider this case as a HI group due 
the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
\end{lstlisting}
\normalsize
\caption{Warning captured as LO priority.}
\label{fig:hi-priority}
\end{figure}

% no-bug low console output
\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
\end{lstlisting}
\normalsize
\caption{Warning captured as HI priority.}
\label{fig:lo-priority}
\end{figure}

@@

\subsection{ES6 design}
\Fix{to appear}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed}
  \begin{tabular}{ccr}
    \toprule
    Name & URL & \# Stars \\
    \midrule
    MS's Chakra & \cite{chakra2018repo} & - \\
    Google's v8 & \cite{v82018repo} & - \\
    Mozilla's SpiderMonkey & \cite{spidermonkey2018repo} & - \\
    Apple's JavaScriptCore (WebKit) & \cite{jsc2018repo} & - \\
   \bottomrule     
  \end{tabular}
\end{table}

>>>>

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries.
\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}
\Igor{seems like an API. They define the language behavior; grammar;
values to static variables; the methods for each "class"(Object)...
These irregularities appears on engine implementation, 
maybe an wrong if statement and so on.}
We found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that,
the function \CodeIn{Number.toPrecision(precision)}, in general,
if precision is defined the method returns a String 
containing the Number value represented either 
in decimal exponential notation or in decimal 
fixed notation~\cite{es6-toPrecision}. The Number object uses a 
property that the specification describes as approximately so when we use 
toPrecision with a bigger precision, the values of each engine may vary, this
could be considered as a case of incompatibility by engine design.}
In those cases, our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category.
\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
due the capacity of a fuzzer add an infinite repetition statement. We expected that
each test process can running utmost 5 seconds, if exceed this condition we stop 
the process and add a output message of a TIMEOUT error.}

\Mar{show real examples of
  HI and LO. Use the stacktraces to explain what is going on.}

@@

% bug high console output
% This a case of a warning reported as HI priority, the Figure~\ref{} shows
% the output console of V8 engine. We consider this case as a HI group due 
% the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}

% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function, 
%     typeof, return, throw, new, Error, if},
%   }
%   \begin{lstlisting}
% \end{lstlisting}
% \normalsize
% \caption{Warning captured as LO priority.}
% \label{fig:hi-priority}
% \end{figure}

% no-bug low console output
% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function, 
%     typeof, return, throw, new, Error, if},
%   }
%   \begin{lstlisting}
% \end{lstlisting}
% \normalsize
% \caption{Warning captured as HI priority.}
% \label{fig:lo-priority}
% \end{figure}

@@

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed}
  \begin{tabular}{ccr}
    \toprule
    Name & URL & \# Stars \\
    \midrule
    MS's Chakra & \cite{chakra2018repo} & 7200+ \\
    Google's v8 & \cite{v82018repo} & 9800+ \\
    Mozilla's SpiderMonkey & \cite{spidermonkey2018repo} & - \\
    Apple's JavaScriptCore (WebKit) & \cite{jsc2018repo} & - \\
    Mozilla's Rhino & \cite{rhino2018repo} & 1800+ \\
    JerryScript's JerryScript & \cite{jerryscript2018repo} & 3100+ \\
   \bottomrule     
  \end{tabular}
\end{table}
